Highlighting Disputed Claims on the Web

### 2010-02-10 papers/www_disputefinder/disputefinder_final.tex
Spell check

Client side entailment gets the most coverage, but the worst precision. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they are posted. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites. The flip side is that the classification algorithm needs to be simple enough to run on the client without noticably slowing down the web browser, and the algorithm is limited to only being able to use whatever data can be downloaded to the client.

@@

To improve performance, rather than running the LLM algorithm for every pair of sentences and paraphrases, we compare each sentence with every paraphrase simultaneously by searching for words in order of their rareness. For each paraphrase, we sort the words in order of their rareness in Wikipedia, and then assemble a set that contains the rarerst word in every known paraphrase. If a sentence contains one of these rare words, we create a (memoized) set that contains the second-rarest word that appears in each of the paraphrases that contained the first word and then check whether the sentence contains any of these words. We repeat this process until we find a claim paraphrase such that all the non stop-words in the paraphrase are contained in the sentence.

The combination of a simple algorithm and a optimized implementation allows us to check for textual entailment between every sentence on every page a user browses and every claim paraphrase in our database with only moderate slowdown. On a 2.33Ghz Core2 processor, Dispute Finder is able to check for disputed claims on the New York Times front page in 50 milliseconds, and is able to check the Wikipedia page on Global Warming in 127 milliseconds. Moreover, to further hide this latency from users, Dispute Finder checks for disputed claims asynchronously in the background rather than forcing the user to wait. Note however that these figures are for a database with only 2,609 disputed claims. It remains to be seen how our algorithm will scale to a database with millions of disputed claims.

>>>>

Client side entailment gets the most coverage, but the worst precision. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they are posted. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites. The flip side is that the classification algorithm needs to be simple enough to run on the client without noticeably slowing down the web browser, and the algorithm is limited to only being able to use whatever data can be downloaded to the client.

@@

To improve performance, rather than running the LLM algorithm for every pair of sentences and paraphrases, we compare each sentence with every paraphrase simultaneously by searching for words in order of their rareness. For each paraphrase, we sort the words in order of their rareness in Wikipedia, and then assemble a set that contains the rarest word in every known paraphrase. If a sentence contains one of these rare words, we create a (memoized) set that contains the second-rarest word that appears in each of the paraphrases that contained the first word and then check whether the sentence contains any of these words. We repeat this process until we find a claim paraphrase such that all the non stop-words in the paraphrase are contained in the sentence.

The combination of a simple algorithm and a optimized implementation allows us to check for textual entailment between every sentence on every page a user browses and every claim paraphrase in our database with only moderate slowdown. On a 2.33GHz Core2 processor, Dispute Finder is able to check for disputed claims on the New York Times front page in 50 milliseconds, and is able to check the Wikipedia page on Global Warming in 127 milliseconds. Moreover, to further hide this latency from users, Dispute Finder checks for disputed claims asynchronously in the background rather than forcing the user to wait. Note however that these figures are for a database with only 2,609 disputed claims. It remains to be seen how our algorithm will scale to a database with millions of disputed claims.
